Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-21 manuscript.Rmd
Test full pipeline from raw data

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

@@

```{r IMfig, fig.cap="Summary of intermodulation responses in pupillometry (a) and EEG (b). The data are from the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\\%. Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies. Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.", out.width = '50%', fig.align="center", echo=FALSE}

>>>>

processdata <- 3  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

@@

```{r IMfig, fig.cap="Summary of intermodulation responses in pupillometry (a) and EEG (b) data. The data are pooled across the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\\%. Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies (red). Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.", out.width = '50%', fig.align="center", echo=FALSE}
